The Hosting Environment of the Advanced Resource Connector middleware

### 2008-08-30 doc/hed/ARCHED_article.tex
More of HED documentation.

@@

@@

The HED defines few lifetimes for operations happening inside the Chain and components which can be associated with them:

@@

\item The Session lifetime - is defined by existence of some logical connection between Messages being processed. Corresponding container MessageContext is normally created by first MCC in a chain. Actual lifetime of that container is MCC specific. For TCP MCC it corresponds to TCP connection. The MessageContext holds objects inherited from MessageContextElement class. When Session ends all associated objects are destroyed.

%\item The Session Context. It holds objects inherited from MessageContextElement class and is persistent withion

@@

@@

In order to facilitate the developement of services, API bindings for languages other than C++ are provided and some service developement has already been done 
%Not much aboút the actual services, more about what they need to implement and what

The chain formulation using MCCs is up to the administrator.  Based on the configuration information the Loader components formulate the actual chain in the memory of the daemon.

@@

@@

The server TCP MCC in the HED is special in that it produces messages by listening on a socket rather than passing on messages from other MCCs. As such it spawns new threads to handle the message and its response throughout the message chain. One could envision other parallel MCCs having these properties but producing messages from other sources such as e.g. unix sockets.

@@

\section{Implemented PDCs}

>>>>

\chapter{How to read}

This document does not (yet?) include in depth description of C++ classes which constitute the HED. Instead most section contain notes entitled "Relevant classes". Technical description of those classes can be found in automatically generated "Hosting Environment (Daemon) Reference Manual" document [].

For examples please see source code in repository []. Many components and libraries are accompanied with test and example applications.

@@

\texttt{Relevant classes: Arc::Plexer }

@@

\texttt{Relevant classes: Arc::MessageContext, Arc::MessageContextElement, Arc::MessageAuthContext, Arc::ChianContext }

The HED defines three lifetimes for operations happening inside the Chain and components which can be associated with them:

@@

\item The Session lifetime - is defined by existence of some logical connection between Messages being processed. Corresponding container MessageContext is normally created by first MCC in a chain and attached to the Message. Actual lifetime of that container is MCC specific. For TCP MCC it corresponds to TCP connection. The MessageContext holds objects inherited from MessageContextElement class. The Security Attributes can also be stored in dedicated container - MessageAuthContext - with Session lifetime. At end of  the Session all associated objects are destroyed.

\item The Chain lifetime - is time period while componnets making the Chain exist. This lifetime is represented by ChainContext class. Differently from other context objects this one doe not allow free manipulation of contained objects. Instead it provides an interface to some internal structures of Loader object. Those include factories and lists of object of all types created by particular instance of the Loader.

@@

\subsection{DMC}

\texttt{Relevant classes: Arc::DataPoint, Arc::DataMover and related classes.}

The HED defines an interface for pluggable components implementing higher-level information transfer and query. Those are Data Management Components (DMC). Each DMC is inherited from Datapoint class and provides subset of methods for performing following operations on data endpoint:

\item Read data from specified endpoint into DataBuffer class object

\item Write data into specified endpoint from DataBuffer class object

\item List subcontent of endpoint (i.e. list files in directory)

\item Register and unregister presence of data

The DMC may be implemented using third party software like it is currently done for (Grid)FTP DMC. But implementation may use Message Chains too like in case of HTTP MCC.

Along with ordinary endpoints defining location of data directly - like HTTP, FTP, LDAP - the DMC can be used with indirect/indexing endpoints. Those are endpoints which define only location of meta-data associated with actual data or an interface/service providing functionality of managing/requesting data.

% TODO a lot

@@

In order to facilitate the developement of services, API bindings for languages other than C++ are provided and some service developement has already been done in Python language.

% TODO it

@@

This chapter describes components which are implemented alongside with the HED infractructure itself. Although strictly not belonging to infrastructure this minimal set of components is necessary to make inrastructure useful.

@@

The server TCP MCC in the HED is special in that it produces messages by listening on a network socket rather than passing on messages from other MCCs. As such it spawns new thread for every new connection to handle Messages and their responses throughout the Message Chain. One could envision other MCCs having these properties but producing messages from other sources such as e.g. unix sockets.

@@

\section{Implemented DMCs}

\subsection{File DMC}

\subsection{GridFTP/FTP DMC}

\subsection{HTTP DMC}

\subsection{LDAP DMC}

\subsection{LFC DMC}

\subsection{RLS DMC}
